The Evolution of National AS Chokepoints and Their Connection to Internet Freedom

### 2018-06-29 Paper/paper.tex
updated draft

\begin{document}
\raggedbottom
\maketitle
\begin{multicols}{2}

@@

% Rest of Paper Layout
\par

@@

The AS-layer of the Internet is the highest level of organization of the Internet. ASes generally represent ISP networks,
large university networks, or government entities. Interdomain routing between these ASes is governed by BGP, and
individual ASes may have local preferences for how they wish to send packets along, but they cannot govern the paths
selected by other ASes. AS topology researchers often use measurement tools to create a picture of the global Internet.
These measurement tools, for instance BGP Updates from BGPStream \cite{BGPStream} or empirical paths from traceroute \cite{traceroute}, suffer from
incompleteness and innacuracies \cite{tracerouteProblems}.
\par
AS-level studies are further complicated by the lack of ground truth data for AS relationships and BGP paths. For AS relationships,
inference is often used based on economic considerations to classify the relationships of ASes. This was first done by Gao \cite{gao} by
maximizing the occurances of certain economic rules on the AS graph by choosing a particular set or relationships. This technique was only
evaluated against a single ISPs set of true relationships, however. As part of the CAIDA project, this inference technique was extended, leading
to the CAIDA AS-relationship dataset \cite{CAIDApaper}, \cite{CAIDA}. We choose these relationships for our purposes, and they are the current
research standard.
\par
Finding BGP paths is more of a challenge. Packet based simulations, wherein BGP is simulated directly, are computationally infeasible for the
scales relevant to a global study. An accurate, but realistic, simulation technique must be chosen to provide useful research potential in this regard.
The BGPSim algorithm \cite{quicksand} is one such simulation technique that is suitable for this study's purposes. BGPSim takes a set of AS relationships
as input, such as those provided by the CAIDA dataset \cite{CAIDA}, and returns routing trees based off of these relationships. These paths are found via
a modified breadth-first seach (BFS) algorithm. The BFS adds edges to routing trees first according to local preference (LP), then shortest path (SP), and finally tiebreak (TB).
A resulting routing tree contains all the equally reasonable paths (according to economic concerns) that exist between source ASes (within the routing tree) to 
destination ASes (the root of the routing tree). We find this technique suitable for our purposes, so we extend BGPSim 
(in ways explained further in this paper) as part of \toolname.

@@

\par
In order to compare multiple nations, we have plotted the number of ASes needed to intercept 90\% of in-to-out paths
for each timestamp recorded. These results are detailed in figure \ref{fig:nodes}.

@@

>>>>

\begin{document}
\maketitle
\begin{multicols}{2}

@@

% Rest of Paper Layout
\par
The layout of the rest of this paper is as follows: Section 3 provides relavent background information
to the problems we are investigating; Section 4 introduces and defines the measure of chokepoint
potential; Section 5 details our tool for simulating and evaluating AS topologies \toolname; Section 6
explains our experimental setups; Sections 7, 8, and 9 provide results, discussion, and related work
respectively.

@@

The AS-layer of the Internet is the highest level of organization of the Internet. ASes generally represent ISP networks,
large university networks, or government entities. Interdomain routing between these ASes is governed by BGP, and
individual ASes may have local preferences for how they wish to send packets along, but they cannot govern the paths
selected by other ASes. AS topology researchers often use measurement tools to create a picture of the global Internet.
These measurement tools, for instance BGP Updates from BGPStream \cite{BGPStream} or empirical paths from traceroute, suffer from
incompleteness and innacuracies \cite{tracerouteProblems}.
\par
AS-level studies are further complicated by the lack of ground truth data for AS relationships and BGP paths. For AS relationships,
inference is often used based on economic considerations to classify the relationships of ASes. This was first done by Gao \cite{gao} by
maximizing the occurances of certain economic rules on the AS graph by choosing a particular set or relationships. This technique was only
evaluated against a single ISPs set of true relationships, however. As part of the CAIDA project, this inference technique was extended, leading
to the CAIDA AS-relationship dataset \cite{CAIDApaper}, \cite{CAIDA}. We choose these relationships for our purposes, and they are the current
research standard.
\par
Finding BGP paths is more of a challenge. Packet based simulations, wherein BGP is simulated directly, are computationally infeasible for the
scales relevant to a global study. An accurate, but realistic, simulation technique must be chosen to provide useful research potential in this regard.
The BGPSim algorithm \cite{quicksand} is one such simulation technique that is suitable for this study's purposes. BGPSim takes a set of AS relationships
as input, such as those provided by the CAIDA dataset \cite{CAIDA}, and returns routing trees based off of these relationships. These paths are found via
a modified breadth-first seach (BFS) algorithm. The BFS adds edges to routing trees first according to local preference (LP), then shortest path (SP), and finally tiebreak (TB).
A resulting routing tree contains all the equally reasonable paths (according to economic concerns) that exist between source ASes (within the routing tree) to 
destination ASes (the root of the routing tree). We find this technique suitable for our purposes, so we extend BGPSim 
(in ways explained further in this paper) as part of \toolname.

@@

\par
In order to compare multiple nations, we have plotted the number of ASes needed to intercept 90\% of in-to-out paths
for each timestamp recorded. These results are detailed in figure \ref{fig:nodes}.
The distinct behaviors of each nation are rather striking. We can see a steep decline for some
nations known to limit Internet freedom (China and Iran) as well as the increase for other nations
(Germany and Brazil). Other nations have stayed more stable. It is worth pointing out that if a nation
has required the same number of border ASes to control many paths over several years, this suggests
that the chokepoints have grown to intercept more paths. The reason for this is that the number of ASes,
and thus the number of paths, has increased globally over time. This fact makes the decline in ASes
needed for some nations even more glaring.

@@

% Chokepoint Potential
In this paper we have introduced a novel measure, chokepoint potential, that allows us to
evaluate the level of difficulty that a government faces when trying to censor the Internet
based entirely on AS-level topology. Our technique for evaluating chokepoint potential using
\toolname provides a monitoring capability of BGP dynamics that was previously not possible.
We have taken advantage of efficient simulation, standard AS relationship datasets, and cross-platform
design principles so that this tool is readily deployable for future research.
% Ecolution over time
\par
Our application of \toolname to investigate evolutions in the global AS graph over time shows us
interesting trends in AS topologies.
% Internet Freedom
\par
We have validated chokepoint potential as having a relationship to actual censorship by showing
the significance of the relationship between the chokepoint potential of nations and their FOTN
score from freedom house.
